---
title: "Queuing_envelope_mg1"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
date: "2024-04-24"
---
# Approximating Queuing Delay from M/GI/1 to M/M/1 Envelope
```{r setup, include=FALSE}
library(simmer)
library(ggplot2)
set.seed(4321)
```

## FUNCTIONS

```{r include=FALSE}
envelope_cdf <- function(rate) {
  exp_values <- rexp(1e4, rate = rate)
  empirical_cdf <- ecdf(exp_values)
  return(empirical_cdf)
}
#M/G/1 simmer delay simulation
simmer_mg1 <- function(Capacity_Gbps, Load, PS_size, PS_weights, k_num){
  
  N = sum(PS_size*PS_weights)
  N
  nodes_capacity_Bps = Capacity_Gbps*1e9
  
  env <- simmer()
  
  env %>% add_resource("node_1", 1)
  
  trajectory_1_2 <- trajectory() %>%
    seize("node_1") %>%
    timeout(function() 8*sample(PS_size, size = 1, replace = T, prob = PS_weights)/nodes_capacity_Bps) %>%
    release("node_1")
  
  Capacity_ps = Capacity_Gbps*1e9/(8*N)
  traffic_val = Capacity_Gbps*1e9*Load/(8*N)
  
  # Define arrival process
  env %>%
    add_generator("trajectory_1_2", trajectory_1_2, function() rexp(1, traffic_val))
  
  
  env %>% run(until = 11000/traffic_val)
  
  all_arrivals_res <- data.frame(env %>%
                                   get_mon_arrivals(per_resource = FALSE) %>%
                                   transform(waiting_time_in_queue = round(end_time - start_time - activity_time)) %>%
                                   transform(spending_time = end_time - start_time))
  
  return(all_arrivals_res$spending_time[1:k_num])
}
```

### Function for Calculating of M/M/1 envelope load for M/G/1
```{r cars}
envelope_load_calc <- function(Capacity_Gbps, k_num, Load, PS_size, PS_weights)
{
  mg1_packets <- simmer_mg1(Capacity_Gbps, Load, PS_size, PS_weights, k_num = 1e4)
  cat("Load real M/G/1:", Load, "\n")
  
  # Step 1: Determine the average delay (E(T)) 
  E_T_real <- mean(mg1_packets) 
  N = sum(PS_size*PS_weights)
  N
  var_N <- sum(PS_size^2*PS_weights) - N^2
  Cs2 <- var_N/(N^2)
  nodes_capacity_Bps = Capacity_Gbps*1e9
  Capacity_ps = nodes_capacity_Bps/(8*N)
  E_X = 1/Capacity_ps
  
  percentiles_seq <- seq(0.5, 0.99, 0.01)
  
  n = 1
  df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
  rho_env = seq(from=0.01,to=0.99,by=0.01)
  for (rho in rho_env){
    df_env <- qexp(percentiles_seq,rate = ((1-rho)/E_X))*1e6 # mu s
    if (all(df_real < df_env)){
      cat("Envelope upper bound \n")
      cat("Load Envelope:", rho, "\n")
      cat("E(T) exponential envelope M/M/1:", E_X/(1-rho), "s \n")
      cat("E(T) Real M/GI/1:", E_T_real, "s \n")
      cat("\n")
      break
    }
    n = n + 1
  }
  return(rho)
}

```

## INPUT DATA

```{r pressure, echo=TRUE, message=TRUE, warning=FALSE}

Capacity_Gbps = 10
k_num = 1e4 #number of simulation packages
Load <- 0.7  # Load
# #V1
PS_size <- c(40, 576, 1500)  # Packet sizes in bytes
PS_weights <- c(7, 4, 1) / 12  # Packet weights

```

```{r include=FALSE}

#V2 https://www.ams-ix.net/ams
# PS_size=c((64+127)/2,(128+255)/2,(256+511)/2, (512+1023)/2, (1024+1513)/2, 1514, (1515+9100)/2)
# PS_weights=c(33.2/100, 5.4/100, 3.3/100, 3.7/100, 34.6/100, 14.6/100, 5.2/100)


#V3 https://www.seattleix.net/statistics/
# PS_size=c((64), (65+128)/2, (129+256)/2,(257+384)/2, (385+512)/2,(513+640)/2,(641+768)/2,(769+896)/2,
#           (897+1024)/2,
#           (1025+1152)/2,(1153+1280)/2,(1515+1408)/2,(1409+1536)/2, (1537+9999)/2)
# PS_weights = c(4.2, 22.73, 4.79,1.93,0.92, 1.04, 0.74, 0.49, 0.45, 0.82, 6.56,9.30, 45.95, 0.07)
# PS_weights=PS_weights/100

# #V4 https://grafana.sfmix.org/public-dashboards/7dedd014679f4c798124748a24e9f5ef?orgId=1&from=now-2d&to=now
# PS_size=c(64,
#           (65+127)/2,
#           (128+255)/2,
#           (256+511)/2,
#           (513+1023)/2,
#           (1024+1517)/2,
#           (1518+9999)/2)
# PS_weights = c(2, 23, 5, 5, 5, 40, 20)
# PS_weights=PS_weights/100
```
# Part 1: simulation M/G/1 and envelope M/M/1 calculations

## SIMULATION

```{r}
mg1_packets <- simmer_mg1(Capacity_Gbps, Load, PS_size, PS_weights, k_num = 1e4)
```

## M/G/1 calculations of parameters

```{r}
real_cdf <- ecdf(mg1_packets)
cat("Load real M/G/1:", Load, "\n")

# Step 1: Determine the average delay (E(T)) 
E_T_real <- mean(mg1_packets) 
N = sum(PS_size*PS_weights)
N
var_N <- sum(PS_size^2*PS_weights) - N^2
Cs2 <- var_N/(N^2)
nodes_capacity_Bps = Capacity_Gbps*1e9
Capacity_ps = nodes_capacity_Bps/(8*N)
E_X = 1/Capacity_ps
```

## Envelope M/M/1 fitting process

Envelope E(T) M/M/1 should be above real M/G/1 for percentiles from 50% - 99% 
```{r}
percentiles_seq <- seq(0.5, 0.99, 0.01)

n = 1
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
rho_env = seq(from=0.01,to=0.99,by=0.01)
for (rho in rho_env){
  df_env <- qexp(percentiles_seq,rate = ((1-rho)/E_X))*1e6 # mu s
  if (all(df_real < df_env)){
    cat("Envelope upper bound \n")
    cat("Load Envelope:", rho, "\n")
    cat("E(T) exponential envelope M/M/1:", E_X/(1-rho), "s \n")
    cat("E(T) Real M/GI/1:", E_T_real, "s \n")
    break
  }
  n = n + 1
}

rho_env = rho
envelope_rate = (1-rho)/E_X

```

## Plots

PDF of real and envelope
```{r}
plot(density(mg1_packets*1e6), col = "blue", main = "", xlab = "Delay, μs", lwd = 2)
lines(density(rexp(1e4, rate = envelope_rate)*1e6), col = "darkgreen", lwd = 2)
legend("topright", legend = c("M/G/1", "M/M/1"), col = c("blue", "darkgreen"), lwd = 2)
grid()
```

Plot the percentiles of real and envelope
```{r}
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))
df_env <- sapply(percentiles_seq, function(x) quantile(rexp(1e4, rate = envelope_rate), x))

# Plot with no additional x-axis labels
plot(df_real, col = "blue", xlab = "", ylab = "Delay Quantile, s", main = "", xaxt = "n", lwd = 2)
lines(df_real, col = "blue", lwd = 2)
lines(df_env, col = "darkgreen", lwd = 2)

# Add x-axis labels for percentiles_seq
axis(1, at = seq_along(percentiles_seq), labels = paste0(percentiles_seq * 100, "%"))
legend("topleft", legend = c("M/G/1", "M/M/1"), col = c("blue", "darkgreen"), lwd = 2)
grid()
```

Plot the log CCDF
```{r}

t_min = min(mg1_packets)
t_max = 2*E_T_real
# Compute the empirical CDF
ecdf_values <- ecdf(mg1_packets)
# Generate x values for the plot E(T)
x_values <- seq(t_min, t_max, length.out = 1e4)
# Compute the empirical CDF values
ecdf_y_values_sim <- ecdf_values(x_values)


envelope_ecdf_val <- envelope_cdf(envelope_rate)
ecdf_y_values_env_upper_bound <- envelope_ecdf_val(x_values)


lwd = 4
plot(x_values, log10(1 - ecdf_y_values_sim), type = "l", xlab = "Delay, s", ylab = "log CCDF", main = "", col = "blue", lwd = lwd)
lines(x_values, log10(1 - ecdf_y_values_env_upper_bound), col = "darkgreen", lty = 2, lwd  = lwd )
legend("topright", legend = c(paste("real CCDF ρ = ", Load),
                             paste("Envelope CCDF ρ =", round(rho_env, 2))),
      col = c("blue", "darkgreen" ), lty = c(1, 2), lwd = 2)

grid()
```

# Part 2: finding polinomial regression/relationship between load_real and load_envelope

```{r}
# Data
loads_real <- seq(0.01, 0.99, 0.01)
loads_envelope <- sapply(loads_real, function(load) envelope_load_calc(Capacity_Gbps, k_num, load, PS_size, PS_weights)) 

# Fitting a quadratic polynomial regression model
model <- lm(loads_envelope ~ poly(loads_real, 2, raw = TRUE))

# Generating sequence of loads_real values for prediction
load_real_pred <- seq(min(loads_real), max(loads_real), length.out = 100)

# Predicting loads_envelope values for the generated loads_real values
load_envelope_pred <- predict(model, newdata = data.frame(loads_real = load_real_pred))

# Plotting the observed data and the predicted values
plot(loads_real, loads_envelope, type = 'l', col = 'deepskyblue4', xlab = expression(rho[M/GI/1]), ylab = expression(rho[envelope]), main = 'Quadratic Polynomial Regression', lwd = 2)
lines(load_real_pred, load_envelope_pred, col = 'green', lwd = 2)
grid()
legend("bottomright",c("Observ.","Predicted"), 
       col=c("deepskyblue4","green"), lwd=3)

```

Extract the coefficients from the fitted quadratic polynomial regression model:


```{r}
# Extract the coefficients of the fitted model
coef_model <- coef(model)

# Construct the formula
formula <- paste0("y(x) = ", coef_model[1], " + ", coef_model[2], "x", 
                  " + ", coef_model[3], "x^2")

# Print the formula
print(formula)
```

# Part 3: Checking the polinomial prediction
```{r}
loads_real = 0.57
cat("Load real M/G/1:", loads_real, "\n")

mg1_packets <- simmer_mg1(Capacity_Gbps, loads_real, PS_size, PS_weights, k_num = 1e4)


load_envelope_predicted = predict(model, newdata = data.frame(loads_real))


n = 1
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
rho_env = seq(from=0.01,to=0.99,by=0.01)

df_env <- qexp(percentiles_seq,rate = ((1-load_envelope_predicted)/E_X))*1e6 # mu s
cat("All quantiles df_real are below envelope:", all(df_real < df_env), "\n")
cat("Envelope upper bound \n")
cat("Load envelope M/M/1:", load_envelope_predicted, "\n")
cat("E(T) exponential envelope M/M/1:", E_X/(1-load_envelope_predicted), "s \n")
cat("E(T) Real M/GI/1:", mean(mg1_packets), "s \n")
    

```

```{r}
print(paste0("Envelope load obtained from polynomial: ", formula,"=",coef_model[1] +coef_model[2]*loads_real + coef_model[3]*loads_real^2))
```
# Part 4:
## Polynomial prediction for different packet size distributions 
```{r echo=TRUE, message=FALSE}
# Data
#V1
PS_size <- c(40, 576, 1500)  # Packet sizes in bytes
PS_weights <- c(7, 4, 1) / 12  # Packet weights
loads_real <- seq(0.01, 0.99, 0.01)

loads_envelope_v1 <- sapply(loads_real, function(load) envelope_load_calc(Capacity_Gbps, k_num, load, PS_size, PS_weights)) 

# Fitting a quadratic polynomial regression model
model_v1 <- lm(loads_envelope_v1 ~ poly(loads_real, 2, raw = TRUE))

# Generating sequence of loads_real values for prediction
load_real_pred <- seq(min(loads_real), max(loads_real), length.out = 100)

# Predicting loads_envelope values for the generated loads_real values
load_envelope_pred_v1 <- predict(model_v1, newdata = data.frame(loads_real = load_real_pred))

#V2 https://www.ams-ix.net/ams
PS_size=c((64+127)/2,(128+255)/2,(256+511)/2, (512+1023)/2, (1024+1513)/2, 1514, (1515+9100)/2)
PS_weights=c(33.2/100, 5.4/100, 3.3/100, 3.7/100, 34.6/100, 14.6/100, 5.2/100)
loads_envelope_v2 <- sapply(loads_real, function(load) envelope_load_calc(Capacity_Gbps, k_num, load, PS_size, PS_weights)) 
model_v2 <- lm(loads_envelope_v2 ~ poly(loads_real, 2, raw = TRUE))
load_envelope_pred_v2 <- predict(model_v2, newdata = data.frame(loads_real = load_real_pred))

#V3 https://www.seattleix.net/statistics/
# PS_size=c((64), (65+128)/2, (129+256)/2,(257+384)/2, (385+512)/2,(513+640)/2,(641+768)/2,(769+896)/2,
#           (897+1024)/2,
#           (1025+1152)/2,(1153+1280)/2,(1515+1408)/2,(1409+1536)/2, (1537+9999)/2)
# PS_weights = c(4.2, 22.73, 4.79,1.93,0.92, 1.04, 0.74, 0.49, 0.45, 0.82, 6.56,9.30, 45.95, 0.07)
# PS_weights = PS_weights/100

# #V4 San Francisco Metropolitan Internet Exchange (SFMIX) https://grafana.sfmix.org/public-dashboards/7dedd014679f4c798124748a24e9f5ef?orgId=1&from=now-2d&to=now
PS_size=c(64,
          (65+127)/2,
          (128+255)/2,
          (256+511)/2,
          (513+1023)/2,
          (1024+1517)/2,
          (1518+9999)/2)
PS_weights = c(2, 23, 5, 5, 5, 40, 20)
PS_weights=PS_weights/100

loads_envelope_v3 <- sapply(loads_real, function(load) envelope_load_calc(Capacity_Gbps, k_num, load, PS_size, PS_weights)) 
model_v3 <- lm(loads_envelope_v3 ~ poly(loads_real, 2, raw = TRUE))
load_envelope_pred_v3 <- predict(model_v3, newdata = data.frame(loads_real = load_real_pred))

```

```{r}
plot(load_real_pred, load_envelope_pred_v1, type = 'l', col = 'blue', xlab = expression(rho[real]), ylab = expression(rho[env]),# main = 'Quadratic Polynomial Regression',
     lwd = 3, ylim = c(0,1), cex.lab = 1.5)
lines(loads_real, loads_envelope_v1, col = 'blue', lwd = 1, lty= 1)
lines(load_real_pred, load_envelope_pred_v2, col = 'darkgreen', lwd = 2)
lines(loads_real, loads_envelope_v2, col = 'darkgreen', lwd = 1, lty= 1)
lines(load_real_pred, load_envelope_pred_v3, col = 'red', lwd = 2)
lines(loads_real, loads_envelope_v3, col = 'red', lwd = 1, lty= 1)
lines(loads_real, loads_real, col = 'black', lwd = 2, lty= 4)
# Add labels for the vertical lines with rotated text
legend_text_v1 <- bquote("Tri-modal: " ~ rho[env] ~ "=" ~ .(round(coef_model_v1[1], 2)) ~ "+" ~ .(round(coef_model_v1[2], 2)) * rho[real] ~ "+" ~ .(round(coef_model_v1[3], 2)) * rho[real]^2)

legend_text_v2 <- bquote("AMS-IX: " ~ rho[env] ~ "=" ~ .(round(coef_model_v2[1], 2)) ~ "+" ~ .(round(coef_model_v2[2], 2)) * rho[real] ~ "+" ~ .(round(coef_model_v2[3], 2)) * rho[real]^2)

legend_text_v3 <- bquote("SFMIX: " ~ rho[env] ~ "=" ~ .(round(coef_model_v3[1], 2)) ~ "+" ~ .(round(coef_model_v3[2], 2)) * rho[real] ~ "+" ~ .(round(coef_model_v3[3], 2)) * rho[real]^2)

text(0.25, 0, 
     legend_text_v1,
     col = "blue", pos = 4, srt = 0)
text(0.25, 0.1,
     legend_text_v2,
     col = "darkgreen", pos = 4, srt = 0)
text(0.25, 0.2,
     legend_text_v3,
     col = "red", pos = 4, srt = 0)
text(0.3, 0.35,
     expression(paste(rho[real], "=", rho[env])),
     col = "black", pos = 4, srt = 25)



grid()
```


# Part 5: Checking the polinomial prediction for V4


```{r}
#V4 San Francisco Metropolitan Internet Exchange (SFMIX) https://grafana.sfmix.org/public-dashboards/7dedd014679f4c798124748a24e9f5ef?orgId=1&from=now-2d&to=now
PS_size=c(64,
          (65+127)/2,
          (128+255)/2,
          (256+511)/2,
          (513+1023)/2,
          (1024+1517)/2,
          (1518+9999)/2)
PS_weights = c(2, 23, 5, 5, 5, 40, 20)
PS_weights=PS_weights/100

loads_real = 0.6
cat("Load real M/G/1:", loads_real, "\n")

mg1_packets <- simmer_mg1(Capacity_Gbps, loads_real, PS_size, PS_weights, k_num = 1e4)


load_envelope_predicted = predict(model_v3, newdata = data.frame(loads_real))


n = 1
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
rho_env = seq(from=0.01,to=0.99,by=0.01)

df_env <- qexp(percentiles_seq,rate = ((1-load_envelope_predicted)/E_X))*1e6 # mu s
cat("All quantiles df_real are below envelope:", all(df_real < df_env), "\n")
cat("Envelope upper bound \n")
cat("Load envelope M/M/1:", load_envelope_predicted, "\n")
cat("E(T) exponential envelope M/M/1:", E_X/(1-load_envelope_predicted), "s \n")
cat("E(T) Real M/GI/1:", mean(mg1_packets), "s \n")
    

```

# Part 6: Envelope load obtained from polynomial v1,v2,v3
V1 c(40, 576, 1500)
```{r}
# Extract the coefficients of the fitted model
coef_model_v1 <- coef(model_v1)
# Construct the formula
formula <- paste0("y(x) = ", coef_model_v1[1], " + ", coef_model_v1[2], "x", 
                  " + ", coef_model_v1[3], "x^2")
# Print the formula
print(formula)
```

Calculating RMSE (Root Mean Square Error) and R-squared for V1:
```{r}
rmse_v1 <- sqrt(mean((loads_envelope_v1 - predict(model_v1))^2))
r2_v1 <- summary(model_v1)$r.squared
```

V2 AMS-IX Amsterdam https://www.ams-ix.net/ams
```{r}

# Extract the coefficients of the fitted model
coef_model_v2 <- coef(model_v2)
# Construct the formula
formula <- paste0("y(x) = ", coef_model_v2[1], " + ", coef_model_v2[2], "x", 
                  " + ", coef_model_v2[3], "x^2")
# Print the formula
print(formula)

```
Calculating RMSE and R-squared for V2:
```{r}
rmse_v2 <- sqrt(mean((loads_envelope_v2 - predict(model_v2))^2))
r2_v2 <- summary(model_v2)$r.squared
```

V3 San Francisco Metropolitan Internet Exchange (SFMIX)
```{r}

# Extract the coefficients of the fitted model
coef_model_v3 <- coef(model_v3)
# Construct the formula
formula <- paste0("y(x) = ", coef_model_v3[1], " + ", coef_model_v3[2], "x", 
                  " + ", coef_model_v3[3], "x^2")
# Print the formula
print(formula)

```
Calculating RMSE and R-squared for V3:
```{r}
rmse_v3 <- sqrt(mean((loads_envelope_v3 - predict(model_v3))^2))
r2_v3 <- summary(model_v3)$r.squared
```

# Part 7: Calculate the average coefficients for the polynomial models using rounding.

```{r}
c = round(coef_model_v3[1], 2)
b = round(coef_model_v3[2], 2)
a = round(coef_model_v3[3], 2)

formula <- paste0("y(x) = ", c, " + ", b, "x", " + ", a, "x^2")

print(formula)
```
# Part 8: Each model's performance.

Compare the performance of the individual polynomial models  the average polynomial model with the average polynomial model by calculating the RMSE and R-squared metrics
```{r}
cat("Model v1: RMSE =", rmse_v1, ", R^2 =", r2_v1, "\n")
cat("Model v2: RMSE =", rmse_v2, ", R^2 =", r2_v2, "\n")
cat("Model v3: RMSE =", rmse_v3, ", R^2 =", r2_v3, "\n")
# Calculate RMSE and R^2 for the average polynomial model
load = seq(0.01,0.99,0.01)
polinomial_pred_v3 <- a*load^2 + b*load + c#(predict(model_v1) + predict(model_v2) + predict(model_v3))/3

rmse_avg_v1 <- sqrt(mean((loads_envelope_v1 - polinomial_pred_v3)^2))
r2_avg_v1 <- summary(lm(loads_envelope_v1 ~ polinomial_pred_v3))$r.squared

rmse_avg_v2 <- sqrt(mean((loads_envelope_v2 - polinomial_pred_v3)^2))
r2_avg_v2 <- summary(lm(loads_envelope_v2 ~ polinomial_pred_v3))$r.squared

rmse_avg_v3 <- sqrt(mean((loads_envelope_v3 - polinomial_pred_v3)^2))
r2_avg_v3 <- summary(lm(loads_envelope_v3 ~ polinomial_pred_v3))$r.squared
cat("V3 Polynomial compare with Model Model v1: RMSE =", rmse_avg_v1, ", R^2 =", r2_avg_v1, "\n")
cat("V3 Polynomial compare with Model Model v2: RMSE =", rmse_avg_v2, ", R^2 =", r2_avg_v2, "\n")

```
Mean Absolute Percent Error (MAPE), coefficient of variation (CV) , Mean absolute error (MAE)
```{r}
# Mean Absolute Percentage Error (MAPE)
mape <- function(forecast, actual) {
  return(mean(abs((actual - forecast) / actual)) * 100)
}

# Mean Absolute Error (MAE)
mae <- function(forecast, actual) {
  return(mean(abs(actual - forecast)))
}
```

Mean Absolute Percent Error (MAPE), coefficient of variation , Mean absolute error
```{r}
# Calculate metrics for each model
loads_real <- seq(0.01, 0.99, 0.01)

mape_v1 <- mape(predict(model_v1), loads_envelope_v1)
mae_v1 <- mae(predict(model_v1), loads_envelope_v1)

mape_v2 <- mape(predict(model_v2), loads_envelope_v2)
mae_v2 <- mae(predict(model_v2), loads_envelope_v2)

mape_v3 <- mape(predict(model_v3), loads_envelope_v3)
mae_v3 <- mae(predict(model_v3), loads_envelope_v3)

# Calculate metrics for average polynomial model
mape_avg_v1 <- mape(polinomial_pred_v3, loads_envelope_v1)
mae_avg_v1 <- mae(polinomial_pred_v3, loads_envelope_v1)

mape_avg_v2 <- mape(polinomial_pred_v3, loads_envelope_v2)
mae_avg_v2 <- mae(polinomial_pred_v3, loads_envelope_v2)

mape_avg_v3 <- mape(polinomial_pred_v3, loads_envelope_v3)
mae_avg_v3 <- mae(polinomial_pred_v3, loads_envelope_v3)

# Print metrics for each model and average polynomial model
cat("Model v1: MAPE =", mape_v1, ", MAE =", mae_v1, "\n")
cat("Model v2: MAPE =", mape_v2, ", MAE =", mae_v2, "\n")
cat("Model v3: MAPE =", mape_v3, ", MAE =", mae_v3, "\n")
cat("V3 Polynomial Model for V1: MAPE =", mape_avg_v1,", MAE =", mae_avg_v1, "\n")
cat("V3 Polynomial Model for V2: MAPE =", mape_avg_v2,", MAE =", mae_avg_v2, "\n")
```
```{r}
# Plotting the observed data and the predicted values

plot(loads_real, polinomial_pred_v3, type = 'l', col = 'black', xlab = expression(rho[M/GI/1]), ylab = expression(rho[envelope]),# main = 'Quadratic Polynomial Regression',
     lwd = 3, ylim = c(0,1))


grid()
legend("bottomright",c("Polinomial predicted values"), 
        col=c("black"), lwd=3)
```

# Part 9: Second numerc example

## V1 tri-model:
```{r}
# #V1
PS_size <- c(40, 576, 1500)  # Packet sizes in bytes
PS_weights <- c(7, 4, 1) / 12  # Packet weights
Capacity_Gbps = 400
loads <- seq(0.5,0.9,0.05) # Load
p1 = 0.99
p2 = 0.90
E_T_real <-  c()
E_T_real_p1 <-  c()
E_T_real_p2 <-  c()
E_T_env <-  c()
E_T_env_p1 <-  c()
E_T_env_p2 <-  c()
i = 1
for (load in loads){
  mg1_packets <- simmer_mg1(Capacity_Gbps, load, PS_size, PS_weights, k_num = 1e4)
  cat("Load real M/G/1:", load, "\n")
  load_env <- a*load^2 + b*load + c
  
  nodes_capacity_Bps = Capacity_Gbps*1e9
  Capacity_ps = nodes_capacity_Bps/(8*N)
  E_X = 1/Capacity_ps
  
  # Step 1: Determine the average delay (E(T)) 
  E_T_real[i] <- mean(mg1_packets)*1e6
  E_T_real_p1[i] <- quantile(mg1_packets, p1)*1e6
  E_T_real_p2[i] <- quantile(mg1_packets, p2)*1e6
  
  E_T_env[i] <- E_X/(1-load_env)*1e6
  E_T_env_p1[i] <- E_X/(1-load_env)*log(1/(1-p1))*1e6
  E_T_env_p2[i] <- E_X/(1-load_env)*log(1/(1-p2))*1e6
  
  i <- i + 1
}



```
Comparison of theoretical M/M/1 envelope and simulated M/G/1 delays for AMS-IX traffic distribution
```{r}
# Plot the results
plot(loads, E_T_real, type = "l", col = "blue", lwd = 2, xlab = "Load", ylab = "Delay, us", ylim = c(0, max(E_T_real_p1, E_T_env_p1)), main = "")
lines(loads, E_T_env, type = "l", col = "darkgreen", lwd = 2)
lines(loads, E_T_real_p1, type = "l", col = "blue", lwd = 1, lty = 2)
lines(loads, E_T_env_p1, type = "l", col = "darkgreen", lwd = 1, lty = 2)
lines(loads, E_T_real_p2, type = "l", col = "blue", lwd = 1, lty = 3)
lines(loads, E_T_env_p2, type = "l", col = "darkgreen", lwd = 1, lty = 3)

legend("topleft", legend = c("M/G/1 average", "M/M/1 env average", "M/G/1 99th percentile", "M/M/1 env 99th percentile", "M/G/1 90th percentile", "M/M/1 env 90th percentile"), col = c("blue", "darkgreen", "blue", "darkgreen", "blue", "darkgreen"), lwd = c(2, 2, 1, 1, 1, 1), lty = c(1, 1, 2, 2, 3, 3))

grid()

```
## V2 AMS-IX:

```{r}
#V2 https://www.ams-ix.net/ams
PS_size=c((64+127)/2,(128+255)/2,(256+511)/2, (512+1023)/2, (1024+1513)/2, 1514, (1515+9100)/2)
PS_weights=c(33.2/100, 5.4/100, 3.3/100, 3.7/100, 34.6/100, 14.6/100, 5.2/100)

Capacity_Gbps = 400
loads <- seq(0.5,0.9,0.05) # Load
p1 = 0.99
p2 = 0.90
E_T_real <-  c()
E_T_real_p1 <-  c()
E_T_real_p2 <-  c()
E_T_env <-  c()
E_T_env_p1 <-  c()
E_T_env_p2 <-  c()
i = 1
for (load in loads){
  mg1_packets <- simmer_mg1(Capacity_Gbps, load, PS_size, PS_weights, k_num = 1e4)
  cat("Load real M/G/1:", load, "\n")
  load_env <- a*load^2 + b*load + c
  
  nodes_capacity_Bps = Capacity_Gbps*1e9
  Capacity_ps = nodes_capacity_Bps/(8*N)
  E_X = 1/Capacity_ps
  
  # Step 1: Determine the average delay (E(T)) 
  E_T_real[i] <- mean(mg1_packets)*1e6
  E_T_real_p1[i] <- quantile(mg1_packets, p1)*1e6
  E_T_real_p2[i] <- quantile(mg1_packets, p2)*1e6
  
  E_T_env[i] <- E_X/(1-load_env)*1e6
  E_T_env_p1[i] <- E_X/(1-load_env)*log(1/(1-p1))*1e6
  E_T_env_p2[i] <- E_X/(1-load_env)*log(1/(1-p2))*1e6
  
  i <- i + 1
}
```

Comparison of theoretical M/M/1 envelope and simulated M/G/1 delays for AMS-IX traffic distribution
```{r}
# Plot the results
plot(loads, E_T_real, type = "l", col = "blue", lwd = 2, xlab = "Load", ylab = "Delay, us", ylim = c(0, max(E_T_real_p1, E_T_env_p1)), main = "")
lines(loads, E_T_env, type = "l", col = "darkgreen", lwd = 2)
lines(loads, E_T_real_p1, type = "l", col = "blue", lwd = 1, lty = 2)
lines(loads, E_T_env_p1, type = "l", col = "darkgreen", lwd = 1, lty = 2)
lines(loads, E_T_real_p2, type = "l", col = "blue", lwd = 1, lty = 3)
lines(loads, E_T_env_p2, type = "l", col = "darkgreen", lwd = 1, lty = 3)

legend("topleft", legend = c("M/G/1 average", "M/M/1 env average", "M/G/1 99th percentile", "M/M/1 env 99th percentile", "M/G/1 90th percentile", "M/M/1 env 90th percentile"), col = c("blue", "darkgreen", "blue", "darkgreen", "blue", "darkgreen"), lwd = c(2, 2, 1, 1, 1, 1), lty = c(1, 1, 2, 2, 3, 3))

grid()

```


