---
title: "Queuing_envelope_mg1"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
date: "2024-04-24"
---
# Approximating Queuing Delay from M/GI/1 to M/M/1 Envelope
```{r setup, include=FALSE}
library(simmer)
library(ggplot2)
set.seed(4321)
```

## FUNCTIONS

```{r include=FALSE}
envelope_cdf <- function(rate) {
  exp_values <- rexp(1e4, rate = rate)
  empirical_cdf <- ecdf(exp_values)
  return(empirical_cdf)
}
#M/G/1 simmer delay simulation
simmer_mg1 <- function(Capacity_Gbps, Load, PS_size, PS_weights, k_num){
  
  N = sum(PS_size*PS_weights)
  N
  nodes_capacity_Bps = Capacity_Gbps*1e9
  
  env <- simmer()
  
  env %>% add_resource("node_1", 1)
  
  trajectory_1_2 <- trajectory() %>%
    seize("node_1") %>%
    timeout(function() 8*sample(PS_size, size = 1, replace = T, prob = PS_weights)/nodes_capacity_Bps) %>%
    release("node_1")
  
  Capacity_ps = Capacity_Gbps*1e9/(8*N)
  traffic_val = Capacity_Gbps*1e9*Load/(8*N)
  
  # Define arrival process
  env %>%
    add_generator("trajectory_1_2", trajectory_1_2, function() rexp(1, traffic_val))
  
  
  env %>% run(until = (k_num+1e3)/traffic_val)
  
  all_arrivals_res <- data.frame(env %>%
                                   get_mon_arrivals(per_resource = FALSE) %>%
                                   transform(waiting_time_in_queue = round(end_time - start_time - activity_time)) %>%
                                   transform(spending_time = end_time - start_time))
  
  return(all_arrivals_res$spending_time[1:k_num])
}
```

### Function for Calculating of M/M/1 envelope load for M/G/1
```{r cars}
envelope_load_calc <- function(Capacity_Gbps, k_num, Load, PS_size, PS_weights)
{
  mg1_packets <- simmer_mg1(Capacity_Gbps, Load, PS_size, PS_weights, k_num = 1e4)
  cat("Load real M/G/1:", Load, "\n")
  
  # Step 1: Determine the average delay (E(T)) 
  E_T_real <- mean(mg1_packets) 
  N = sum(PS_size*PS_weights)
  N
  var_N <- sum(PS_size^2*PS_weights) - N^2
  Cs2 <- var_N/(N^2)
  nodes_capacity_Bps = Capacity_Gbps*1e9
  Capacity_ps = nodes_capacity_Bps/(8*N)
  E_X = 1/Capacity_ps
  
  percentiles_seq <- seq(0.5, 0.99, 0.01)
  
  n = 1
  df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
  rho_env = seq(from=0.01,to=0.99,by=0.01)
  for (rho in rho_env){
    df_env <- qexp(percentiles_seq,rate = ((1-rho)/E_X))*1e6 # mu s
    if (all(df_real < df_env)){
      cat("Envelope upper bound \n")
      cat("Load Envelope:", rho, "\n")
      cat("E(T) exponential envelope M/M/1:", E_X/(1-rho), "s \n")
      cat("E(T) Real M/GI/1:", E_T_real, "s \n")
      cat("\n")
      break
    }
    n = n + 1
  }
  return(rho)
}

```

## INPUT DATA

```{r pressure, echo=TRUE, message=TRUE, warning=FALSE}

Capacity_Gbps = 10
k_num = 1e6 #number of simulation packages
Load <- 0.7  # Load
# # #V1
# PS_size <- c(40, 576, 1500)  # Packet sizes in bytes
# PS_weights <- c(7, 4, 1) / 12  # Packet weights

```

```{r include=FALSE}

#V2 https://www.ams-ix.net/ams
# PS_size=c((64+127)/2,(128+255)/2,(256+511)/2, (512+1023)/2, (1024+1513)/2, 1514, (1515+9100)/2)
# PS_weights=c(33.2/100, 5.4/100, 3.3/100, 3.7/100, 34.6/100, 14.6/100, 5.2/100)
# 

#V3 https://www.seattleix.net/statistics/
# PS_size=c((64), (65+128)/2, (129+256)/2,(257+384)/2, (385+512)/2,(513+640)/2,(641+768)/2,(769+896)/2,
#           (897+1024)/2,
#           (1025+1152)/2,(1153+1280)/2,(1515+1408)/2,(1409+1536)/2, (1537+9999)/2)
# PS_weights = c(4.2, 22.73, 4.79,1.93,0.92, 1.04, 0.74, 0.49, 0.45, 0.82, 6.56,9.30, 45.95, 0.07)
# PS_weights=PS_weights/100

#V4 https://grafana.sfmix.org/public-dashboards/7dedd014679f4c798124748a24e9f5ef?orgId=1&from=now-2d&to=now
PS_size=c(64,
          (65+127)/2,
          (128+255)/2,
          (256+511)/2,
          (513+1023)/2,
          (1024+1517)/2,
          (1518+9999)/2)
PS_weights = c(2, 23, 5, 5, 5, 40, 20)
PS_weights=PS_weights/100
```
# Part 1: simulation M/G/1 and envelope M/M/1 calculations

## SIMULATION

```{r}
mg1_packets <- simmer_mg1(Capacity_Gbps, Load, PS_size, PS_weights, k_num)
```

## M/G/1 calculations of parameters

```{r}
real_cdf <- ecdf(mg1_packets)
cat("Load real M/G/1:", Load, "\n")

# Step 1: Determine the average delay (E(T)) 
E_T_real <- mean(mg1_packets) 
N = sum(PS_size*PS_weights)
N
var_N <- sum(PS_size^2*PS_weights) - N^2
Cs2 <- var_N/(N^2)
nodes_capacity_Bps = Capacity_Gbps*1e9
Capacity_ps = nodes_capacity_Bps/(8*N)
E_X = 1/Capacity_ps
E_T_real_theor <- E_X*Load/(1-Load)*(1+Cs2)/2
D_T_real_theor_90 <- (E_X*Load/(1-Load)*(1+Cs2)/2 + E_X)*log(1/(1-0.90))
D_T_real_theor_99 <- (E_X*Load/(1-Load)*(1+Cs2)/2 + E_X)*log(1/(1-0.99))

#sqrt(var_N)
```

## Envelope M/M/1 fitting process

Envelope E(T) M/M/1 should be above real M/G/1 for percentiles from 50% - 99% 
```{r}
percentiles_seq <- seq(0.5, 0.99, 0.01)

n = 1
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets, x))*1e6 #real
rho_env = seq(from=0.01,to=0.99,by=0.01)
for (rho in rho_env){
  df_env <- qexp(percentiles_seq,rate = ((1-rho)/E_X))*1e6 # mu s
  if (all(df_real < df_env)){
    cat("Envelope upper bound \n")
    cat("Load Envelope:", rho, "\n")
    cat("E(T) exponential envelope M/M/1:", E_X/(1-rho), "s \n")
    cat("E(T) Real M/GI/1:", E_T_real, "s \n")
    break
  }
  n = n + 1
}

rho_env = rho
envelope_rate = (1-rho)/E_X

```

## Plots

PDF of real and envelope
```{r}
plot(density(mg1_packets*1e6), col = "blue", main = "", xlab = "Delay, μs", lwd = 2)
lines(density(rexp(1e4, rate = envelope_rate)*1e6), col = "darkgreen", lwd = 2)
legend("topright", legend = c("M/G/1 SFMIX", "M/M/1 envelope"), col = c("blue", "darkgreen"), lwd = 2)
grid()
```
```{r}
# # Assuming mg1_packets and envelope_rate are already defined
# 
# # Plot the histogram of mg1_packets with density option
# hist(mg1_packets * 1e6, breaks = 50, probability = TRUE, col = "#9393ff", main = "", xlab = "Delay, μs", ylim = c(0, max(density(mg1_packets * 1e6, bw = 0.25)$y - 0.05)), border = "blue")
# 
# # Add the density line for mg1_packets
# #lines(density(mg1_packets * 1e6), col = "blue", lwd = 2)
# 
# # Add the density line for the exponential distribution (envelope)
# dens_env <- density(rexp(1e4, rate = envelope_rate) * 1e6, bw = 0.25)
# dens_env$x[dens_env$x<0] <- 0
# lines(dens_env, col = "darkgreen", lwd = 2)
# 
# # Add the legend
# legend("topright", legend = c("M/G/1 SFMIX", "M/M/1 envelope"), col = c("#9393ff", "darkgreen"), lwd = c(20,2))
# 
# # Add the grid
# grid()

```


```{r}
lambda <- rho * 1/E_X
# Theoretical M/M/1 delay density function
mm1_delay_density <- function(d, lambda, mu) {
  rho <- lambda / mu
  lambda * (1 - rho) * exp(-lambda * (1 - rho) * d)
}

# Define the range of delay values for plotting
delay_values <- seq(0, 50e-6, length.out = 1000)

# Compute the theoretical density values
density_values <- mm1_delay_density(delay_values, lambda, 1/E_X)


```


```{r}
# Assuming mg1_packets, E_X, and rho are defined

# Compute lambda based on rho and E_X
lambda <- rho * 1/E_X

# Theoretical M/M/1 delay density function
mm1_delay_density <- function(d, lambda, mu) {
  rho <- lambda / mu
  lambda * (1 - rho) * exp(-lambda * (1 - rho) * d)
}

xlimit =  40e-6 #s
# Define the range of delay values for plotting
delay_values <- seq(0, xlimit, length.out = 1000)

# Compute the theoretical density values
density_values <- mm1_delay_density(delay_values, lambda, 1/E_X)

# Plot the histogram of mg1_packets with density option
hist(mg1_packets * 1e6, breaks = 50, probability = TRUE, col = "#9393ff", main = "", xlab = "Delay, μs", ylim = c(0, max(density(mg1_packets * 1e6, bw = 0.25)$y - 0.05)), xlim = c(0,xlimit*1e6), border = "blue")

lines(delay_values * 1e6, density_values / 1e6, type = "l", col = "darkgreen", lwd = 2,
      xlab = "Delay (μs)", ylab = "Density", main = "Theoretical M/M/1 Delay Distribution")

# Add vertical lines for mean, 0.90 quantile, and 0.99 quantile of mg1_packets
mean_delay <- mean(mg1_packets) * 1e6
quantile_90 <- quantile(mg1_packets, p = 0.9) * 1e6
quantile_99 <- quantile(mg1_packets, p = 0.99) * 1e6

abline(v = mean_delay, col = "blue", lty = 2, lwd = 2)
abline(v = quantile_90, col = "blue", lty = 2, lwd = 2)
abline(v = quantile_99, col = "blue", lty = 2, lwd = 2)

mean_delay = round(mean_delay, 2)
quantile_90 = round(quantile_90, 2)
quantile_99 = round(quantile_99, 2)


# Add labels for the vertical lines with rotated text
text(mean_delay, par("usr")[4] * 0.4, expression(paste("E(D"[real], ") = ", 5.34, " μs")), col = "blue", pos = 4, srt = 90)
text(quantile_90, par("usr")[4] * 0.4, expression(paste("D"[0.90, real], " = ", 12.44 , " μs")), col = "blue", pos = 4, srt = 90)
text(quantile_99, par("usr")[4] * 0.2, expression(paste("D"[0.99, real], " = ", 24.77 , " μs")), col = "blue", pos = 4, srt = 90)

# Add the legend
legend("topright", legend = c(expression("M/G/1"[SFMIX]), expression("M/M/1"[env])), col = c("#9393ff", "darkgreen"), lwd = c(20, 2))

# Add the grid
grid()

```


Plot the percentiles of real and envelope
```{r}
df_real <- sapply(percentiles_seq, function(x) quantile(mg1_packets*1e6, x))
df_env <- sapply(percentiles_seq, function(x) quantile(rexp(1e5, rate = envelope_rate), x)*1e6)

# Plot with no additional x-axis labels
plot(df_real, col = "#8585ff", xlab = "Quantile, %", ylab = "Delay Quantile, μs", main = "", xaxt = "n", lwd = 2)
lines(df_real, col = "#8585ff", lwd = 2)
lines(df_env, col = "darkgreen", lwd = 2)

# Add x-axis labels for percentiles_seq
axis(1, at = seq_along(percentiles_seq), labels = paste0(percentiles_seq * 100, "%"))
legend("topleft", legend = c("M/G/1 SFMIX", "M/M/1 envelope"), col = c("#8585ff", "darkgreen"), lwd = 2)
grid()
```

Plot the log CCDF
```{r}

t_min = min(mg1_packets)
t_max = 2*E_T_real
# Compute the empirical CDF
ecdf_values <- ecdf(mg1_packets)
# Generate x values for the plot E(T)
x_values <- seq(t_min, t_max, length.out = 1e4)
# Compute the empirical CDF values
ecdf_y_values_sim <- ecdf_values(x_values)


envelope_ecdf_val <- envelope_cdf(envelope_rate)
ecdf_y_values_env_upper_bound <- envelope_ecdf_val(x_values)


lwd = 4
plot(x_values, log10(1 - ecdf_y_values_sim), type = "l", xlab = "Delay, s", ylab = "log CCDF", main = "", col = "blue", lwd = lwd)
lines(x_values, log10(1 - ecdf_y_values_env_upper_bound), col = "darkgreen", lty = 2, lwd  = lwd )
legend("topright", legend = c(paste("real CCDF ρ = ", Load),
                             paste("Envelope CCDF ρ =", round(rho_env, 2))),
      col = c("blue", "darkgreen" ), lty = c(1, 2), lwd = 2)

grid()
```
